---
title: "Lab 04"
author: "Raja Uzair Saeeed & Daniel Persson"
date: "10/12/2021"
output: 
  pdf_document: 
    fig_width: 5
    fig_height: 7

vignette: >
  %\VignetteEngine{knitr::knitr}
  %\VignetteIndexEntry{Lab 04}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Introduction

**Lab 04** package handles the linear regression models. We used the **QR decomposition** method to create the most basic functionality in the R package. We also implement an object oriented system using ***S3 Classes*** to handle special functions such as `print(), plot(), resid(), pred(), coef()`and `summary()`. This package takes two arguments `formula` and `data set`and creates a `linreg`object.

## 2. Functions

In this section, I'll explain all the function of this package with example.

#### 2.1 `linreg`

linreg is the main function that computes the different parameters needed for regression model like `'Regression Coefficients', 'Fitted Values', 'Standard Error'` etc.

Example:

```{r}
library(Lab04)
lm<- linreg(formula = Petal.Length ~ Species, data = iris)
```

#### 2.2 `print.linreg`

This function takes linreg object and print out the coefficients and coefficient names.

Example:

```{r}
library(Lab04)
lm<- linreg(formula = Petal.Length ~ Species, data = iris)
print(lm)
```

\newpage

#### 2.3 `plot.linreg`

This function takes linreg object and plot the regression residuls.

Example:

```{r}
library(Lab04)
lm<- linreg(formula = Petal.Length ~ Species, data = iris)
plot(lm)
```

#### 2.4 `resid.linreg`

This function takes linreg object and returns the vector of residuals.

Example:

```{r}
library(Lab04)
lm<- linreg(formula = Petal.Length ~ Species, data = iris)
head(resid(lm))
```

#### 2.5 `pred.linreg`

This function takes linreg object and return the predicted values.

Example:

```{r}
library(Lab04)
lm<- linreg(formula = Petal.Length ~ Species, data = iris)
head(pred(lm))
```

#### 2.6 `coef.linreg`

This function takes linreg object and return the predicted values.

Example:

```{r}
library(Lab04)
lm<- linreg(formula = Petal.Length ~ Species, data = iris)
coef(lm)
```
